The Proofs

### 2023-11-13 proofs/tex/upgrade-lemmas.tex
Fix margins

    $ 
    \begin{aligned}
        [[fv iQ]] &\subseteq [[fv [pnbs/pnas]iP ∩ fv [pncs/pnas]iP]]
                  &&\text{since by \cref{lemma:fv-propagation}, 
                         $[[fv iQ ⊆ fv [pnbs/pnas]iP]]$ and
                         $[[fv iQ ⊆ fv [pncs/pnas]iP]]$}\\
                  &\subseteq [[ ((fv iP \ {pnas}) ∪ {pnbs}) ∩ ((fv iP \ {pnas}) ∪ {pncs})]]\\
                  &= [[ (fv iP \ {pnas}) ∩ (fv iP \ {pnas}) ]]
                  &&\text{since $[[pnbs]]$ and $[[pncs]]$ are fresh}\\
                  &= [[ fv iP \ {pnas} ]]\\
                  &\subseteq [[ Γ \ {pnas} ]]
                  &&\text{since $[[iP]]$ is well-formed in $[[Γ]]$}\\
                  &\subseteq [[ {Δ} ]]\\
    \end{aligned}
    $\\
    This way, by \cref{lemma:wf-ctxt-equiv}, $[[Δ ⊢ iQ]]$.

>>>>

    $ 
    \begin{aligned}
        [[fv iQ]] &\subseteq [[fv [pnbs/pnas]iP ∩ fv [pncs/pnas]iP]]
                  &&\text{since by \cref{lemma:fv-propagation}, 
                         $[[fv iQ ⊆ fv [pnbs/pnas]iP]]$}\\
                  & &&  \text{and $[[fv iQ ⊆ fv [pncs/pnas]iP]]$}\\
                  &\subseteq [[ ((fv iP \ {pnas}) ∪ {pnbs}) ∩ ((fv iP \ {pnas}) ∪ {pncs})]]\\
                  &= [[ (fv iP \ {pnas}) ∩ (fv iP \ {pnas}) ]]
                  &&\text{since $[[pnbs]]$ and $[[pncs]]$ are fresh}\\
                  &= [[ fv iP \ {pnas} ]]\\
                  &\subseteq [[ Γ \ {pnas} ]]
                  &&\text{since $[[iP]]$ is well-formed in $[[Γ]]$}\\
                  &\subseteq [[ {Δ} ]]\\
    \end{aligned}
    $\\
    This way, by \cref{lemma:wf-ctxt-equiv}, $[[Δ ⊢ iQ]]$.
